Bird beak's elaboration and innovation

### 2022-10-25 Analysis/03.1-Elaboration_innovation_analysis[statistics].Rmd
Update 03.1-Elaboration_innovation_analysis[statistics].Rmd

@@

## Adding starts here and there
get.signif <- function(prob) {
    if(prob >= 0.99) {
        return("***")
    } else {
        if(prob >= 0.95) {
            return("**")
        } else {
            if(prob >= 0.90) {
                return("*")
            } else {
                if(prob >= 0.80) {
                    return(".")
                } else {
                    return("")
                }
            }
        }
    }
}
add.stars <- function(data, counter, shift = 0, total, ...) {
    text(data[3] + 0.03, (total+1)-counter + shift + 0.2, labels = get.signif(data[6]), cex = 1, ...)   
}
add.line <- function(data, counter, shift = 0, total, pch = 19, lty = 1, ...) {
    lines(matrix(c(data[4:5], rep((total+1)-counter + shift, 2)), 2, 2), lty = lty, ...)
    points(data[3], (total+1)-counter + shift, pch = pch,  ...)
}

## Add the number of species and sd to the group names
convert.spaces <- function(x, max) {
    # shifts <- max-nchar(as.character(x))
    # if(shifts > 0) {
    #     return(paste(c(x, rep(" ", shifts)), collapse = ""))
    # } else {
    #     return(x)
    # }
    return(x)
}
group_names <- paste0(plot_table$Group, " (n = ", sapply(plot_table$n, convert.spaces, max = 4), " ; sd = ", sapply(round(plot_table$`ellipse sd`, 2), convert.spaces, max = 5), ")")

@@

@@

## Adding the n2 results
families_n2_plot <- families_n2[match(families[order(families$orthogonality, decreasing = TRUE), ]$Group, families_n2$Group), ]
for(i in 1:nrow(families_n2_plot)) {
    add.line(families_n2_plot[i, ], shift = -1/3, counter = i+nrow(sub_orders), col = adjustcolor(colours[i+nrow(sub_orders)], alpha.f = 2/3), total = nrow(plot_table), lty = 2, pch = 21)
    add.stars(families_n2_plot[i, ], shift = -1/3, counter = i+nrow(sub_orders), col = adjustcolor(colours[i+nrow(sub_orders)], alpha.f = 2/3), total = nrow(plot_table))
}

>>>>

## Adding orders and families that don't have a higher level covered
if(any(no_match <- is.na(match(orders_n2$Group, orders$Group)))) {
    fill_in <- orders_n2[which(no_match), ]
    fill_in[,c(3:8)] <- NA
    orders <- rbind(orders, fill_in)
}
## Adding orders and families that don't have a higher level covered
if(any(no_match <- is.na(match(families_n2$Group, families$Group)))) {
    fill_in <- families_n2[which(no_match), ]
    fill_in[,c(3:8)] <- NA
    families <- rbind(families, fill_in)
}

@@

## Adding stars and thingies here and there
get.signif <- function(prob) {
    if(prob >= 0.99) {
        return("***")
    } else {
        if(prob >= 0.95) {
            return("**")
        } else {
            if(prob >= 0.90) {
                return("*")
            } else {
                if(prob >= 0.80) {
                    return(".")
                } else {
                    return("")
                }
            }
        }
    }
}
add.stars <- function(data, counter, shift = 0, total, ...) {

    text(data[3] + 0.03, (total+1)-counter + shift + 0.2, labels = get.signif(data[6]), cex = 1, ...)   
}
add.line <- function(data, counter, shift = 0, total, pch = 19, lty = 1, ...) {

    lines(matrix(c(data[4:5], rep((total+1)-counter + shift, 2)), 2, 2), lty = lty, ...)
    points(data[3], (total+1)-counter + shift, pch = pch,  ...)
}
convert.spaces <- function(x, max) {

    # shifts <- max-nchar(as.character(x))
    # if(shifts > 0) {
    #     return(paste(c(x, rep(" ", shifts)), collapse = ""))
    # } else {
    #     return(x)
    # }
    return(x)
}

## Set up the group names
group_names <- paste0(plot_table$Group, " (n = ", sapply(plot_table$n, convert.spaces, max = 4), " ; sd = ", sapply(round(plot_table$`ellipse sd`, 2), convert.spaces, max = 5), ")")

@@

## Plot frame
par(mar = c(5, 17, 4, 2))
plot(NULL, yaxt = "n", xaxt = "n", ylab = "", xlab = "orthogonality", ylim = c(1,nrow(plot_table)), xlim = c(0,1))
abline(v = 0.5, lwd = 0.5, col = "grey")
abline(v = 0.75, lty = 2, col = "grey", lwd = 0.5)
axis(2, at = nrow(plot_table):1, labels = group_names[plot_order], las = 2)
axis(1, at = c(0, 0.5, 1), labels = c(0, 0.5, 1))
## Adding the results
for(i in 1:nrow(plot_table)) {
    if(!all(is.na(plot_table[plot_order[i], c(3:8)]))) {
        add.line (plot_table[plot_order[i], ], counter = i, col = colours[plot_order[i]], total = nrow(plot_table))
        add.stars(plot_table[plot_order[i], ], counter = i, col = colours[plot_order[i]], total = nrow(plot_table))
    }
}

@@

## Adding the n2 results
families_n2_plot <- families_n2[match(families[order(families$orthogonality, decreasing = TRUE), ]$Group, families_n2$Group), ]
for(i in 1:nrow(families_n2_plot)) {
    if(!all(is.na(plot_table[plot_order[i], c(3:8)]))) {
        add.line(families_n2_plot[i, ], shift = -1/3, counter = i+nrow(sub_orders), col = adjustcolor(colours[i+nrow(sub_orders)], alpha.f = 2/3), total = nrow(plot_table), lty = 2, pch = 21)
        add.stars(families_n2_plot[i, ], shift = -1/3, counter = i+nrow(sub_orders), col = adjustcolor(colours[i+nrow(sub_orders)], alpha.f = 2/3), total = nrow(plot_table))
    }
}
